Numerical trajectory patterns of floating macroalgae

### 2020-12-15 thesis_chapter_3.Rmd
added pca. output updated

@@

```{r distance plot, message=FALSE, warning=FALSE}
dis_plot
```

>>>>

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(ggfortify)

total_end <- total_data %>%
             filter(t == "2018-01-30 00:00:00")

df <- total_end[2:3]
pca_res <- prcomp(df, scale. = TRUE)

autoplot(pca_res, data = total_end, colour = 'type', loadings = TRUE, loading.label = TRUE, frame = TRUE, frame.type = 'norm')
```

@@

```{r distance plot, message=FALSE, warning=FALSE, echo = FALSE}
dis_plot
```
